data_cleaning_longer_period

### 2023-08-28 code/data_cleaning_longer.Rmd
looking at TMSIS only sample, really

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1  ) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

>>>>

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))
